### 2018-07-06 paper/6-engineering.tex
Tweak Frankenbuild figure caption

\begin{figure}
\vspace{-2mm}
\begin{subfigure}[b]{0.25\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-build.pdf}}
\vspace{-1mm}
\caption{Build \cmd{report.txt}}
\end{subfigure}
\begin{subfigure}[b]{0.40\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-clean.pdf}}
\vspace{-1mm}
\caption{Clean up and evict \cmd{main.prof}}
\end{subfigure}
\begin{subfigure}[b]{0.31\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-rebuild.pdf}}
\vspace{-1mm}
\caption{Full rebuild}
\end{subfigure}
\vspace{-2.5mm}
\caption{A Frankenbuild example: (a)~build a profiling report for \cmd{main.exe}
and record deep constructive traces in the cloud, (b)~clean built files locally
and evict \cmd{main.prof} from the cloud storage, (c)~rebuild \cmd{main.prof} by
executing the build task, rebuild \cmd{report.txt} by downloading it from the
cloud, resulting in a Frankenbuild. New and evicted cloud storage entries are
highlighted.\label{fig-frankenbuild}}
\vspace{-3mm}
\end{figure}

>>>>

\begin{figure}
\vspace{-2mm}
\begin{subfigure}[b]{0.25\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-build.pdf}}
\vspace{-1mm}
\caption{Build \cmd{report.txt}}
\end{subfigure}
\begin{subfigure}[b]{0.40\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-clean.pdf}}
\vspace{-1mm}
\caption{Clean up and evict \cmd{main.prof}}
\end{subfigure}
\begin{subfigure}[b]{0.31\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-rebuild.pdf}}
\vspace{-1mm}
\caption{Full rebuild}
\end{subfigure}
\vspace{-2.5mm}
\caption{A Frankenbuild example: (a)~build a profiling report for \cmd{main.exe}
and record deep constructive traces in the cloud, (b)~clean built files locally
and evict \cmd{main.prof} from the cloud storage, (c)~rebuild \cmd{main.prof} by
executing the build task (profiling is non-deterministic, hence the new hash),
rebuild \cmd{report.txt} by downloading it from the cloud, resulting in a
Frankenbuild. New and evicted cloud storage entries are highlighted.
\label{fig-frankenbuild}}
\vspace{-3mm}
\end{figure}
